\documentclass[]{report}


% Title Page
\title{Utilising peer to peer networking for data transfer over the browser}
\author{Dominic Rathbone}


\begin{document}
\maketitle
\tableofcontents


\chapter*{Interim Report}
\section{Project Scope}
\subsection*{Aims and Objectives}
The ultimate objective of my project is to investigate the possibility of data transfer over web browsers, (in particular audio and video streaming) without the need for a centralised client-server architecture, instead opting for a peer to peer architecture. In order to do so, I will need to research this type of networking as well technologies that will allow for the development of this in the browser. In order to test and demonstrate this objective, I plan to  substantiate it in the form of a web application that people can use to both transfer files to someone else as well as stream them if in a suitable format.
\subsection*{Stakeholders}
The stakeholders involved in my project will be myself and the supervisor of my project, Stelios Kapetanakis.
\subsection*{Methods of Communication}
Stelios and I have set up a regular meeting once a week on friday at 4pm. On top of this, we communicate regularly via email and I will keep everything project related in a git repository that Stelios will have access to.
\subsection*{Project Infrastructure}
\subsection*{Quality Analysis}
\subsection*{Specification}
The first intermediate deliverable will be a signalling server that will allow my web application to discover two clients and establish the connection between them.
\section{Methodology}

As a way of tracking the progression of my project, I plan to use kanban. Kanban is a methodology used within software development that allows for rapid development without overloading the developers working on a project. This is done by producing a backlog of tasks which developers then pull from by in a limited amount, normally 1 or 2 at a time and put through the workflow. This workflow tends to be relatively simple in software development and it will be in my case:

	\begin{itemize}
		\item Development
		\item Code Review
		\item Manual Testing
		\item Stakeholder Approval
	\end{itemize}

Peer to peer networking
The entire idea behind my application is based on a one-to-one peer to peer connection between two browsers. Whilst the connection is formed by WebRTC, it does only this, leaving the application to deal with connecting multiple peers together in a “many-to-many” structure resembling a peer to peer network.
A peer to peer network 


\end{document}          
